Growth model analysis 3spp WB

### 2018-12-04 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
changed seq of indVars

#data for running the simulation
simData <- list(
  nReps = 100,#100, #num of mcmc iterations to grab
  numInd = 500 , # number of individual to simulate
  nOccYOY = 3,
  nOccAdult = 7,
  riverIndex = 1 #Levels: west brook < wb jimmy < wb mitchell < wb obear
)

@@

  simData <- updateSimData(simData)
  nB <- getNBetas()
  m <- createMatrices()

  indVars <- getIndVars()

@@

#projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
save( stats3Spp, lm, relImp, anov, elapsed, simData, file = 'D:/projects/linkedModels/data/out/projectionOut.RData')

# if not re-running the sim
# load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')

# temporary while projOut is a list
#stats3Spp <- projOut[[1]]
#simData <- projOut[[6]]

@@

  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')

@@

ggplot(cAll %>% filter(var %in% 2:8), aes((occ), value, color = factor(rowname))) +
  geom_point(size=3) +
  geom_line() +
  geom_vline(xintercept = 3.5) +
  scale_x_continuous('Sampling occasion',
                    breaks = 2:10,
                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
                    ) +
  scale_y_continuous('Coefficients') +
  theme_publication() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')

@@

>>>>

#data for running the simulation
simData <- list(
  nReps = 25,#100, #num of mcmc iterations to grab
  numInd = 500 , # number of individual to simulate
  nOccYOY = 3,
  nOccAdult = 7,
  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
  minSD = -2, #range and step for independent variable values in the sim
  maxSD = 2, 
  step = 1
)
simData$nOcc <- simData$nOccYOY + simData$nOccAdult
simData$indVarSeq = c(-1.5, -0.75, 0, 1.5) #seq(simData$minSD,simData$maxSD,simData$step)

@@

  simData <- updateSimData(simData) # add #season, itersForSim etc data to simData
  nB <- getNBetas() # get number of betas from mcmc[]
  m <- createMatrices()

  indVars <- getIndVars() # get independent variables table, -1.5, 0, 1.5

@@

#projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
save( stats3Spp, lm, relImp, anov, elapsed, simData, file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))

# if not re-running the sim
# load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
# temporary while projOut is a list
# stats3Spp <- projOut[[1]]
# relImpData <- projOut[[3]]
# anovData <- projOut[[4]]
# simData <- projOut[[6]]
# spp <- c('bkt','bnt','ats')

# raw sim data figs
ggplot(stats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),lenMean)) +
  #geom_point(aes(color = factor(ats))) +
  #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
  geom_smooth()+#(bnt + 2)/4 )) +
  geom_smooth(color = 'green', data = stats3Spp[['bnt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0)) +
  facet_grid(temp ~ flow)

@@

##############################  ggsave(paste0('figures/3Spp_WB/relImpOcc',occSelected,'.png'), width = 9, height = 7, units='in')

@@

ggplot(cAll %>% filter(var %in% 2:8, rowname %in% c('bktC','bntC')), aes((occ), value, color = factor(rowname))) +
  geom_point(size=3) +
  geom_line() +
  geom_vline(xintercept = 3.5) +
  scale_x_continuous('Sampling occasion',
                    breaks = 2:10,
                    labels = c('Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn','Winter')
                    ) +
  scale_y_continuous('Coefficients') +
  theme_publication() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
  facet_wrap(~ var, labeller=labeller(var = labelsC))#, scales = 'free')

@@

# trajectories across indep var values for different combinations. Trying to relate to relImp results
#temp
p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(temp))) +
  geom_line(aes(color = factor(temp))) +
  geom_point(aes(color = factor(temp))) +
  facet_wrap(~spp)

#flow
p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
  geom_line(aes(color = factor(flow))) +
  geom_point(aes(color = factor(flow))) +
  facet_wrap(~spp)

#bkt
p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bkt))) +
  geom_line(aes(color = factor(bkt))) +
  geom_point(aes(color = factor(bkt))) +
  facet_wrap(~spp)

#bnt
p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
  geom_line(aes(color = factor(bnt))) +
  geom_point(aes(color = factor(bnt))) +
  facet_wrap(~spp)

#ats
p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(ats))) +
  geom_line(aes(color = factor(ats))) +
  geom_point(aes(color = factor(ats))) +
  facet_wrap(~spp)

multiplot(p1, p2, p3, p4, p5, cols=2)

#temp*flow
ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(flow))) +
  geom_line(aes(color = factor(flow))) +
  geom_point(aes(color = factor(flow))) +
  facet_grid(temp~spp)

#bkt*bnt
ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,lenMeanMean, group = factor(bnt))) +
  geom_line(aes(color = factor(bnt))) +
  geom_point(aes(color = factor(bnt))) +
  facet_grid(bkt~spp)

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
